End-to-end notebook usage example

### 2024-07-28 nbs/concepts/inferenceindynamicalsystems/index.qmd
fix(nbs): pygments -> gruvbox syntax highlighting
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Probabilistic inference in dynamical systems
toc: true
number-sections: true
highlight-style: pygments
csl: ../../bibstyle.csl
lightbox: auto
format:
#   nature-pdf:
#     natbibstyle: sn-nature
#     # classoption:
#     #   - lineno
#     cite-method: citeproc
#     keep-tex: true
  html:
    html-math-method: mathjax
    include-in-header: ../../mathjax.html
#     mainfont: Latin Modern Sans
#     code-fold: false
#     embed-resources: true
#   docx: default
  ipynb: default
format-links: [ipynb]
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
  # keep-ipynb: true
  # keep-md: true
author:
  - name: Pyrovelocity Team
    email: team@pyrovelocity.net
abstract: |
  This notebook provides a discussion and demonstration of one way to proceed in
  performing probabilistic inference in dynamical systems. In particular we prepare 
  and simulate a deterministic dynamical system and then perform probabilistic 
  inference on the latent variables of the system. This illustrates how to combine
  these two approaches, which is essential for understanding Pyro-Velocity.
keywords: [single-cell transcriptomics, probabilistic modeling, dynamical systems, RNA velocity]
bibliography: ../../references.bib
jupyter:
  jupytext:
    cell_metadata_filter: all
    cell_metadata_json: true
    notebook_metadata_filter: all
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: 1.0
      jupytext_version: 1.16.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
  language_info:
    name: python
  rise:
    scroll: true
    theme: black
  toc-autonumbering: true
  toc-showcode: false
  toc-showmarkdowntxt: false
---

>>>>

---
title: Probabilistic inference in dynamical systems
toc: true
number-sections: true
highlight-style: gruvbox
csl: ../../bibstyle.csl
lightbox: auto
format:
#   nature-pdf:
#     natbibstyle: sn-nature
#     # classoption:
#     #   - lineno
#     cite-method: citeproc
#     keep-tex: true
  html:
    html-math-method: mathjax
    include-in-header: ../../mathjax.html
#     mainfont: Latin Modern Sans
#     code-fold: false
#     embed-resources: true
#   docx: default
  ipynb: default
format-links: [ipynb]
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
  # keep-ipynb: true
  # keep-md: true
author:
  - name: Pyrovelocity Team
    email: team@pyrovelocity.net
abstract: |
  This notebook provides a discussion and demonstration of one way to proceed in
  performing probabilistic inference in dynamical systems. In particular we prepare 
  and simulate a deterministic dynamical system and then perform probabilistic 
  inference on the latent variables of the system. This illustrates how to combine
  these two approaches, which is essential for understanding Pyro-Velocity.
keywords: [single-cell transcriptomics, probabilistic modeling, dynamical systems, RNA velocity]
bibliography: ../../references.bib
jupyter:
  jupytext:
    cell_metadata_filter: all
    cell_metadata_json: true
    notebook_metadata_filter: all
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: 1.0
      jupytext_version: 1.16.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
  language_info:
    name: python
  rise:
    scroll: true
    theme: black
  toc-autonumbering: true
  toc-showcode: false
  toc-showmarkdowntxt: false
---

### 2024-07-28 nbs/templates/user_example/user_example.qmd
chore(nbs): interlink introductory pages
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>
fix(nbs): pygments -> gruvbox syntax highlighting
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Pyrovelocity Notebook Usage Example
toc: true
number-sections: true
highlight-style: pygments
csl: bibstyle.csl
lightbox: auto
format:
#   nature-pdf:
#     natbibstyle: sn-nature
#     # classoption:
#     #   - lineno
#     cite-method: citeproc
#     keep-tex: true
  html:
    html-math-method: katex
#     mainfont: Latin Modern Sans
#     code-fold: false
#     embed-resources: true
#   docx: default
  ipynb: default
format-links: [ipynb]
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
  # keep-ipynb: true
  # keep-md: true
author:
  - name: Pyrovelocity Team
    email: team@pyrovelocity.net
abstract: |
  This notebook demonstrates how to run Pyro-Velocity in a Jupyter notebook on
  downsampled data. The results are not expected to be meaningful, but the
  notebook demonstrates the usage workflow with both a short execution time and
  using limited resources. It attempts to support both Google Colab and local or
  remote Jupyter kernel servers. Links to a blank copy of the notebook are 
  provided below.
keywords: [single-cell transcriptomics, probabilistic modeling, dynamical systems, RNA velocity]
bibliography: references.bib
jupyter:
  jupytext:
    cell_metadata_filter: all
    cell_metadata_json: true
    notebook_metadata_filter: all
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: 1.0
      jupytext_version: 1.16.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
  language_info:
    name: python
  rise:
    scroll: true
    theme: black
  toc-autonumbering: true
  toc-showcode: false
  toc-showmarkdowntxt: false
---

@@

>>>>

---
title: End-to-end notebook usage example
toc: true
number-sections: true
highlight-style: gruvbox
csl: bibstyle.csl
lightbox: auto
format:
#   nature-pdf:
#     natbibstyle: sn-nature
#     # classoption:
#     #   - lineno
#     cite-method: citeproc
#     keep-tex: true
  html:
    html-math-method: katex
#     mainfont: Latin Modern Sans
#     code-fold: false
#     embed-resources: true
#   docx: default
  ipynb: default
format-links: [ipynb]
execute: 
  freeze: true
  eval: true
  warning: false
  error: false
  cache: true
  # keep-ipynb: true
  # keep-md: true
author:
  - name: Pyro&thinsp;-Velocity team
    email: team@pyrovelocity.net
abstract: |
  This notebook demonstrates how to run Pyro&thinsp;-Velocity in a Jupyter notebook on
  downsampled data. The results are not expected to be meaningful, but the
  notebook demonstrates the usage workflow with both a short execution time and
  using limited resources. It attempts to support both Google Colab and local or
  remote Jupyter kernel servers. Links to a blank copy of the notebook are 
  provided below.
keywords: [single-cell transcriptomics, probabilistic modeling, dynamical systems, RNA velocity]
bibliography: references.bib
jupyter:
  jupytext:
    cell_metadata_filter: all
    cell_metadata_json: true
    notebook_metadata_filter: all
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: 1.0
      jupytext_version: 1.16.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
  language_info:
    name: python
  rise:
    scroll: true
    theme: black
  toc-autonumbering: true
  toc-showcode: false
  toc-showmarkdowntxt: false
---

@@

See

- [Installation](/guides/installation.qmd) for installation instructions
- [Introduction](/tutorials/introduction.qmd) for a brief overview
- [Contributing](/about/contributing.qmd) for information on how to setup a development environment
